Gaze-dependent evidence accumulation predicts multi-alternative risky choice behaviour

### 2021-02-12 manuscript/manuscript_refs-numbered.tex
moved labels

% Set figure caption widths and fontsize
\usepackage{caption}
\captionsetup{
    width=0.85\textwidth,
    font=footnotesize,
    labelfont=bf,
    labelsep=period,
    justification=justified,
    singlelinecheck=false}

@@

% Fig. 1: Choice task and attribute space
\begin{SCfigure}[0.8]
\centering
\includegraphics[scale=1]{../figures/1-task_stimuli.pdf}
\caption{\textbf{Choice task and attribute space of stimuli.} \textbf{(a)} Choice task. Trials started with a central fixation cross for 1.5 s. Next, three gambles were presented. Participants made a choice by button press, without time limit. Eye movements were recorded during the choice phase. Finally, brief feedback on the choice (but not on the gamble outcome) was displayed. \textbf{(b)} Attribute space. Each gamble is described by two attributes: Probability $p$ and outcome $m$. The core options $A$ and $B$ were presented in every trial, along with one of four decoy alternatives: Compromise decoys ($C_A$ or $C_B$) and asymmetrically dominated decoys ($D_A$ or $D_B$) are expected to elicit compromise and attraction effects, respectively. Dashed lines indicate possible stimulus placements. \textbf{(c)} Exact positions for $C_B$, $A$ and $C_A$ were calibrated for pairwise indifference in separate binary choice estimation blocks for each individual. Differences in outcome between neighbouring alternatives was not less than 2 EUR. Dominated decoys $D_A$ and $D_B$ were always 2\% and 1 EUR worse than $A$ and $B$ respectively.}
\hspace{0.5cm}
\label{fig:task}
\end{SCfigure}

@@

\begin{equation}
    \label{eq:gla:accumulator}
    X_i^{GLA}(n) = \begin{cases}
             (1 - \lambda) \cdot X_i^{GLA}(n - 1) + 1 \cdot x_i^{GLA} &\text{if $i$ fixated}\\
             (1 - \lambda) \cdot X_i^{GLA}(n - 1) + \theta \cdot x_i^{GLA} &\text{otherwise}
             \end{cases}
\end{equation}

@@

\begin{equation}
    \label{eq:utility}
    U(m_i) = m_i^\alpha
\end{equation}

@@

\begin{equation}
    \label{eq:softmax}
    p(x_i) = \frac{e^{\beta x_i}}{\sum_{j \in J}{e^{\beta x_j}}}
\end{equation}

@@

\begin{equation}
    \label{eq:mdft:v}
    V(t) = C M W(t) + \varepsilon(t)
\end{equation}

@@

\begin{equation}
    \label{eq:mdft:p}
    P(t) = SP(t - 1) + V(t)
\end{equation}

@@

\begin{equation}
    \label{eq:mdft:s}
    S = I - \varphi_2 \exp{(-\varphi_1 D^2)}.
\end{equation}

@@

\begin{equation}
    \label{eq:pweighting}
    w(p) = \frac{p^\gamma}{(p^\gamma + (1 - p)^\gamma)^{\frac{1}{\gamma}}}
\end{equation}

@@

\begin{equation}
    \label{eq:bic}
    BIC_m = -2 \ln{(\hat{L})} + \ln{(n_{trials})} k_m
\end{equation}

>>>>

% Set figure caption widths and fontsize
\usepackage{caption}
\captionsetup{
    width=0.85\textwidth,
    font=footnotesize,
    labelfont=bf,
    labelsep=period,
    justification=justified,
    singlelinecheck=false}
\captionsetup[table]{position=bottom}   %% or below

@@

% Fig. 1: Choice task and attribute space
\begin{SCfigure}[0.8]
\centering
\includegraphics[scale=1]{../figures/1-task_stimuli.pdf}
\caption{\textbf{Choice task and attribute space of stimuli.} \textbf{(a)} Choice task. Trials started with a central fixation cross for 1.5 s. Next, three gambles were presented. Participants made a choice by button press, without time limit. Eye movements were recorded during the choice phase. Finally, brief feedback on the choice (but not on the gamble outcome) was displayed. \textbf{(b)} Attribute space. Each gamble is described by two attributes: Probability $p$ and outcome $m$. The core options $A$ and $B$ were presented in every trial, along with one of four decoy alternatives: Compromise decoys ($C_A$ or $C_B$) and asymmetrically dominated decoys ($D_A$ or $D_B$) are expected to elicit compromise and attraction effects, respectively. Dashed lines indicate possible stimulus placements. \textbf{(c)} Exact positions for $C_B$, $A$ and $C_A$ were calibrated for pairwise indifference in separate binary choice estimation blocks for each individual. Differences in outcome between neighbouring alternatives was not less than 2 EUR. Dominated decoys $D_A$ and $D_B$ were always 2\% and 1 EUR worse than $A$ and $B$ respectively.}
\label{fig:task}
\hspace{0.5cm}
\end{SCfigure}

@@

\begin{equation}
  X_i^{GLA}(n) = \begin{cases}
    (1 - \lambda) \cdot X_i^{GLA}(n - 1) + 1 \cdot x_i^{GLA} &\text{if $i$ fixated}\\
    (1 - \lambda) \cdot X_i^{GLA}(n - 1) + \theta \cdot x_i^{GLA} &\text{otherwise}
  \end{cases}
  \label{eq:gla:accumulator}
\end{equation}

@@

\begin{equation}
  U(m_i) = m_i^\alpha
  \label{eq:utility}
\end{equation}

@@

\begin{equation}
  p(x_i) = \frac{e^{\beta x_i}}{\sum_{j \in J}{e^{\beta x_j}}}
  \label{eq:softmax}
\end{equation}

@@

\begin{equation}
  V(t) = C M W(t) + \varepsilon(t)
  \label{eq:mdft:v}
\end{equation}

@@

\begin{equation}
  P(t) = SP(t - 1) + V(t)
  \label{eq:mdft:p}
\end{equation}

@@

\begin{equation}
  S = I - \varphi_2 \exp{(-\varphi_1 D^2)}.
  \label{eq:mdft:s}
\end{equation}

@@

\begin{equation}
  w(p) = \frac{p^\gamma}{(p^\gamma + (1 - p)^\gamma)^{\frac{1}{\gamma}}}
  \label{eq:pweighting}
\end{equation}

@@

\begin{equation}
  BIC_m = -2 \ln{(\hat{L})} + \ln{(n_{trials})} k_m
  \label{eq:bic}
\end{equation}
